Template Master's Thesis

### 2023-08-21 paper.tex
Add combined results

\newpage

@@

In this thesis, we set out to cluster 473,927 addresses observed in Decentraland. Focusing on on-chain data on Ethereum and Polygon, we reduced the set to 137,544 addresses. Depending on various assumptions, we were able to cluster entities interacting through more than one address. Merging the clusters after applying each of the three clustering heuristics and assuming a treshold value of 0.5 for node embedding, we could cluster X addresses to Y entities. Further assuming that all other addresses are single clusters, we argue that the total number of active users during that time frame was Z.

other Limitations -> ENS pairs? Incorporate time-of-day/normalized gas into feature vectors, two step approach
Limitations: various assumptions, possibly false-positives, some clusters may well be undetected.

%Diskutiere alle resultate gemeinsam, vom anfangs set über on-chain und intra-set zu den clusters.

@@

%The conclusion is more shorter and more general: it concisely answers your main research question and makes recommendations based on your overall findings.
%Conclusions section: Re-state the main points in a new concise way that you want your readers to remember.
%CONCLUSION is to write the output of the work/ investigations in summarized form

Assentiar consuetae ha opinionum mentemque ob ii. Ne conflantur de intelligat et me cohibendam. Imaginandi ob to at agnoscerem et mutationum. In methodum ob ii at quicquid lectorum. Procuravi ha dependent ob evidenter tangantur concipere. Immortalem objectivus deo eae rei attingebam ita advertebam quamprimum. Typis patet prius qua nia mem ens. Suppono sim ita pendere nam agnosci quopiam vestiri spondeo dum. Tes illum mundo vetus signa fit talem res his. Assentiar consuetae ha opinionum mentemque ob ii. Ne conflantur de intelligat et me cohibendam. Imaginandi ob to at agnoscerem et mutationum. In methodum ob ii at quicquid lectorum. Procuravi ha dependent ob evidenter tangantur concipere. Immortalem objectivus deo eae rei attingebam ita advertebam quamprimum. Typis patet prius qua nia mem ens. Suppono sim ita pendere nam agnosci quopiam vestiri spondeo dum. Tes illum mundo vetus signa fit talem res his. 
Assentiar consuetae ha opinionum mentemque ob ii. Ne conflantur de intelligat et me cohibendam. Imaginandi ob to at agnoscerem et mutationum. In methodum ob ii at quicquid lectorum. Procuravi ha dependent ob evidenter tangantur concipere. Immortalem objectivus deo eae rei attingebam ita advertebam quamprimum. Typis patet prius qua nia mem ens. Suppono sim ita pendere nam agnosci quopiam vestiri spondeo dum. Tes illum mundo vetus signa fit talem res his.

@@

\subsection{Database}
\label{sec:database}

>>>>

\subsection{Combining clustering results}

Combining the results of self-authorization, learned node embedding and LAND transfers, we can cluster 37.5\% (51,581 out of 137,544) of addresses representing 29,680 entities. \newline
We assume that the unclustered addresses each represent individual entities, a (strict) distance threshold of 0.5 for clustering addresses generated by Role2Vec and remove the 71-address cluster found in self-authorization.
We estimate a total of 115,643 active users during the studied time frame. Among them, 8,483 entities (X \%) interacted with Decentraland through more than one address. The largest entity consists of 499 addresses. The distribution of cluster sizes can be seen in Figure \ref{fig:barplot_clusters}.

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{../figures/cluster-size-distribution.png}
	\caption{Number of clusters by Cluster Size}
	\label{fig:barplot_clusters}
\end{figure}

@@

The goal of this research/thesis was to identify the number of entities represented by the 473,927 addresses observed in Decentraland between. By focusing on Ethereum and Polygon on-chain data, we narrowed down the address set to 137,544. Combining the three clustering heuristics applied, we successfully clustered 37.5\% (51,581) of these addresses into 29,680 entities. \newline
Assuming the remaining addresses each represent individual entities, we estimate a total of 115,643 active users during the studied time frame. Among them, 8,483 entities used more than one address, with the largest entity having 499 addresses. The distribution of cluster sizes can be seen in Figure \ref{fig:barplot_clusters}.

Assumptions: Assumptions: Role2Vec with a distance threshold of 0.5 (strict)
Removed large self-authorization cluster

Most clusters through graph representation learning
Very dependent on threshold
X \% use more than one address
Large address clusters could be some bot behavior

%Limitations: various assumptions, possibly false-positives, some clusters may well be undetected. 
%other Limitations -> ENS pairs? Incorporate time-of-day/normalized gas into feature vectors, two step approach
%Diskutiere alle resultate gemeinsam, vom anfangs set über on-chain und intra-set zu den clusters.

@@

%...Re-state the main points in a new concise way that you want your readers to remember.
%...write the output of the work/ investigations in summarized form
%...intended to help the reader understand why your research should matter to them after they have finished reading the paper.
%...not merely a summary of your points or a re-statement of your research problem but a synthesis of key points. For most essays, one well-developed paragraph is sufficient for a conclusion, although in some cases, a two-or-three paragraph conclusion may be required.

Clustering heuristics -> specific on-chain events, user patterns, graph representation learning
Best -> graph representation learning
Combination as extension

@@

\subsection{Database Schema}
\label{sec:database}
